% !TeX program = lualatex
\documentclass[11pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
% Sets geometric boundaries and font defaults (Noto Sans) for high legibility
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{fontspec}

\usepackage[english, bidi=basic, provide=*]{babel}

\babelprovide[import, onchar=ids fonts]{english}

% Set default/Latin font to Sans Serif in the main (rm) slot
\babelfont{rm}{Noto Sans}

% --- ADDITIONAL PACKAGES ---
\usepackage{amsmath} % Essential for formal mathematical proofs
\usepackage{amssymb}
\usepackage{booktabs} % For professional quality tables
\usepackage{tabularx} % For responsive table widths
\usepackage{hyperref} % Last package to handle document-wide cross-links

% Document Metadata with Patent Pending Status
\title{
    \textbf{Architecting Cognitive Persistence: Integrating CCMA with 768-Dimensional Hyperbolic Manifolds for Centroid-Preserving Memory} \\
    \vspace{0.5cm}
    \large \textbf{Patent Pending} \\
    \small U.S. Provisional Application No. 64/006,354
}

\author{
	Dane Robert Jones \\ 
	\textit{Software Engineering Student, Western Governors University} \\ 
	\textit{Technical SME, Essintial} \\
	Attica, OH $\vert$ \href{mailto:danerjones@gmail.com}{danerjones@gmail.com} $\vert$ ORCID iD: 0009-0003-8014-7298
}
\date{Filed: March 15, 2026}

\begin{document}
	
	\maketitle
	
	\begin{abstract}
		The deployment of long-horizon conversational agents in resource-constrained computing environments is bottlenecked by the quadratic scaling of transformer self-attention and the catastrophic forgetting inherent to standard First-In-First-Out (FIFO) caches. This paper integrates the Conversational Context Management Algorithm (CCMA) with a 768-dimensional Poincaré ball model of hyperbolic geometry to establish a structurally flawless bridge between high-speed localized caches and deeply hierarchical lifelong memory. Operating on a strict Functional Core / Imperative Shell architecture, we define a Semantic-Temporal Modulator to correct Ebbinghaus decay, and mathematically formalize the threat of ``Centroid Collapse'' in standard Euclidean vector aggregation. By synthesizing a deterministic ``Colliding Weights'' trigger, Tangent Space Max-Pooling sequences, and Riemannian Repulsion executed on FPGA/TPU hybrid silicon, this framework ensures that high-entropy semantic peaks are preserved in perpetuity. We further propose mechanisms for biological Sleep Cycle memory consolidation (Wake/NREM/REM) and resolving multi-agent contradictions via Cellular Sheaves, establishing the geometric foundations necessary for persistent, zero-trust cognitive memory in localized edge environments.
	\end{abstract}
	
	\vspace{0.5cm}
	
	\section{Introduction to the Cognitive Bottleneck in Deep Representation Learning}
	The deployment of long-horizon conversational agents and autonomous endpoints in resource-constrained computing environments is fundamentally bottlenecked by the mathematical limitations of transformer-based self-attention mechanisms. As the sequence length of an interaction increases, the computational requirements scale quadratically ($\mathcal{O}(n^2 \cdot d)$). To prevent computational exhaustion and localized Video Random Access Memory (VRAM) overflow, conventional architectures rely on simplistic First-In-First-Out (FIFO) truncation. However, this precipitates catastrophic forgetting, degrading multi-turn reasoning across extended horizons.
	
	To resolve this, external vector databases are utilized as an out-of-core memory substrate. Standard memory architectures predominantly employ Euclidean geometry, embedding semantic representations in flat, 768-dimensional spaces. While Euclidean retrieval is computationally inexpensive, it is mathematically ill-equipped to model deeply branching hierarchical structures. This research report details a robust theoretical framework uniting the Conversational Context Management Algorithm (CCMA)---functioning as a deterministic short-term memory system---with a 768-dimensional Poincaré ball model of hyperbolic geometry for persistent, distortion-free long-term storage. 

    By strictly adhering to a Functional Core / Imperative Shell paradigm, this architecture systematically intercepts the flattening of distinct vector peaks (Centroid Collapse) without sacrificing the explicit structural nuances strictly necessary for advanced cognitive persistence.
	
	\section{The CCMA Short-Term Memory Substrate}
	The CCMA establishes a rigorous, deterministic, bi-temporal memory framework engineered to process interactions as distinct nodes within a continuously evolving Directed Acyclic Graph (DAG). This deliberately decouples cognitive memory routing from the probabilistic generative outputs of Large Language Models (LLMs).
	
	\subsection{Bi-Temporal Modulation and Ebbinghaus Decay}
	Traditional cognitive models utilize the classical Ebbinghaus forgetting curve, where memory decays as a function of chronological time. In asynchronous environments, vast chronological deltas render strict decay useless. We mathematically redefine this decay by calculating an \textit{Effective Time} ($\Delta t_{\text{eff}}$) integrating the chronological delta ($\Delta t$), the semantic cosine similarity ($S_{\text{sim}}$), and a Bayesian Volatility Index ($V_i$):
	
	\begin{equation}
		\Delta t_{\text{eff}} = \Delta t \cdot (1 - S_{\text{sim}})^\gamma \cdot V_i
	\end{equation}
	
	Where $\gamma$ controls the aggressiveness of the semantic anchor. If $S_{\text{sim}} \to 1$ or $V_i \to 0$, retention is mathematically preserved regardless of chronological delay. Conversely, high volatility exponentially accelerates temporal decay, actively prompting the system to verify mutable states rather than hallucinating.
	
	\subsection{Deduplication, Novelty Penalty, and Cache Protection}
	To prevent the exploitation of the temporal modulation loop by redundant payloads, the framework introduces a Novelty Penalty executed via the Echo Coefficient ($E$). Evaluated over a continuous sliding window of $k$ interactions:
	
	\begin{equation}
		E = \frac{1}{k} \sum_{i=1}^{k} S_{\text{sim}}^{(i)}
	\end{equation}
	
	If $E > \tau_{\text{echo}}$, the deterministic routing layer explicitly overrides the semantic retention curve, initiating a Deduplication Eviction to compact redundant nodes and protect the localized hardware budget.
	
	\subsection{Corrective Retrieval-Augmented Generation (CRAG)}
	CCMA utilizes a CRAG Evaluator to assign confidence scores $s_i$ to incoming prompts. Natural continuations ($s_i > \tau_{\text{high}}$) decay normally. Ambiguous scores merge retrieved knowledge. However, random semantic walks ($s_i < \tau_{\text{low}}$) trigger an immediate \textbf{Hard Context Reset}. The preceding topic is compacted into a Summary Bindle, and the active memory array is violently flushed to dedicate VRAM to the newly established semantic trajectory.
	
	\section{The Spatial and Dimensionality Crisis of Deep Representation Learning}
	While CCMA manages context up to local boundaries, the archival of dense nodes necessitates a permanent structured medium. Embedding hierarchically expanding human-agent conversation within a flat Euclidean geometry introduces severe geometric distortions.
	
	\subsection{The Mathematical Limitations of Euclidean Vector Spaces}
	In standard Euclidean geometry, multidimensional volume expands only \textit{polynomially} with respect to its radius. Conversely, a continuous conversational graph grows at an \textit{exponential} rate. Attempting to embed an exponential tree into a polynomial space forcefully crowds peripheral leaf nodes at the extreme boundaries. This destroys the system's capacity to measure similarities; deep historical context becomes indistinguishable from background noise, leading to hallucination and logical collapse.
	
	\subsection{The Poincaré Ball Paradigm for Persistent Hyperbolic Storage}
	To resolve this, the architecture mandates a complete transition to a mathematical manifold possessing constant negative curvature: hyperbolic space. Within the Poincaré ball, spatial volume expands exponentially, rendering it mathematically isometric to hierarchical conversational trees. 
	
	For points within the defined manifold, where $c$ denotes the absolute negative curvature, the distance metric is established as:
	
	\begin{equation}
		d_c(x,y) = \frac{1}{\sqrt{c}}\cosh^{-1}\left(1+2c\frac{\|x-y\|^2}{(1-c\|x\|^2)(1-c\|y\|^2)}\right)
	\end{equation}
	
	This radial distance acts as a deterministically calculable geometric proxy for the Ebbinghaus forgetting curve. Highly salient nodes reside near the origin point. As nodes decay in temporal relevance, they are systematically pushed toward the absolute perimeter, being mathematically ``forgotten'' via exponentially increased metric distance without requiring destructive physical deletion.

    \begin{table}[h]
    \centering
    \caption{Core Spatial Property Disparities}
    \vspace{0.2cm}
    \begin{tabularx}{\textwidth}{>{\hsize=1.2\hsize\bfseries}X >{\hsize=0.9\hsize}X >{\hsize=0.9\hsize}X}
    \toprule
    Geometric Property & Standard Euclidean Space & Hyperbolic Space (Poincaré Ball) \\
    \midrule
    Intrinsic Curvature & $K = 0$ (Absolutely Flat) & $K < 0$ (Constant Negative) \\
    Spatial Volume Expansion & Polynomial Growth Rate & Exponential Growth Rate \\
    Hierarchical Tree Embedding & Extremely High Structural Distortion & Mathematically Minimal Distortion \\
    Primary Distance Metric & L2 Norm / Simple Cosine Similarity & Inverse Hyperbolic Cosine \\
    Knowledge Representation & Dense, Arbitrary Semantic Clustering & Preservation of Directed Acyclic Graphs \\
    \bottomrule
    \end{tabularx}
    \end{table}

	\subsection{The Mechanics of Centroid Collapse and Max-Pooling Dilemmas}
    When generative models summarize a lengthy conversation, functions locate the geometric ``center'' of the data points. In Euclidean systems, continuous averaging yields a heavily flattened, semantically ambiguous representation (e.g., averaging ``kernel diagnostics'' and ``payment methods'' yields a dead void). This is formally defined as \textbf{Centroid Collapse}.
    
    In hyperbolic space, simple element-wise averaging is invalid. Systems rely on the Fréchet mean:
    \begin{equation}
        y = \arg\min_{p\in\mathbb{B}_c^n} \sum_{i=1}^{m} w_i d_c^2(p, x_i)
    \end{equation}
    While elegant, the Fréchet mean suffers from identical semantic flattening. To preserve ``peaks,'' CCMA utilizes \textit{Max-Pooled Semantic Signatures}. However, applying max-pooling directly to coordinates within the Poincaré ball induces severe training instabilities because the operation ignores the non-linear metric tensor.
    
    \subsection{Synthesizing ``Colliding Weights'' as a Deterministic Trigger}
    To reconcile max-pooling with hyperbolic constraints, we synthesize the concept of ``colliding weights'' from hypergraph rendering. A ``weight collision'' occurs when multiple semantically distinct nodes exhibit similar retention weights while located in a highly dense geometric neighborhood.

    The Functional Core evaluates a calculable local collision density potential ($\Phi_{\text{total}}$). If this exceeds a safety threshold, the system declares a state of \textbf{Colliding Weights}, firing a deterministic hardware interrupt that halts the standard Fréchet mean computation.

    \begin{table}[h]
    \centering
    \caption{Deterministic Routing Matrix and Trigger Execution}
    \vspace{0.2cm}
    \begin{tabularx}{\textwidth}{llcX}
    \toprule
    \textbf{System State Variable} & \textbf{Evaluation Condition} & \textbf{Trigger} & \textbf{Execution Pathway} \\
    \midrule
    Spatial Proximity ($D$) & $d_c(x_i,x_j) > \epsilon_d$ & Inactive & Standard Semantic-Temporal Compaction \\
    Retention Weights ($W$) & $w_i \approx w_j$ & - & - \\
    Collision Density ($\Phi$) & $\Phi_{\text{total}} > \tau_{\text{collapse}}$ & \textbf{ACTIVE} & Halt Aggregation, Initiate Tangent Operations \\
    Echo Coefficient ($E$) & $E > \tau_{\text{echo}}$ & \textbf{ACTIVE} & Bypass Geometry, Deduplication Eviction \\
    \bottomrule
    \end{tabularx}
    \end{table}

    \subsection{Mathematical Resolution: Tangent Space Max-Pooling \& Repulsion}
    Once triggered, the Functional Core safely resolves the aggregation via two pathways:
    
    \textbf{Pathway Alpha: Tangent Space Max-Pooling.} The system calculates the Einstein midpoint as a local origin, projects the vectors directly onto the flat \textit{tangent space} via the complex logarithmic map, strictly extracts the highest dimensional peaks using standard Cartesian pooling, and gracefully projects the optimized vector back down onto the curved manifold via the exponential map.
    
    \textbf{Pathway Beta: Riemannian Repulsion.} If nodes must remain distinct, the system applies deterministic tie-breakers (FNV-1a hashes) and injects a repulsive geometric displacement metric (InfoNCE-inspired). This forcefully pushes separated nodes away from the localized centroid, preserving fidelity.

    \section{Asynchronous Memory Consolidation: Biological Sleep Cycles}
    This architecture mimics biological memory consolidation, moving temporary episodic data (hippocampus/L1) to stable neocortex (Poincaré ball). 
    
    \subsection{Mathematical Mapping of Wake, NREM, and REM Phases}
    A dynamic vector $v_i$ is governed by a unified mathematical matrix representing biological states:
    
    \begin{equation}
    \mathcal{M}_{\text{state}}(v_i) =
    \begin{cases}
        \emptyset, & \text{if } \frac{1}{k}\sum_{j=1}^{k}S_{\text{sim}}^{(j)} > \tau_{\text{echo}} \\
        v_i \cdot \exp\left(-\Delta t \cdot (1-S_{\text{sim}})^\gamma \cdot V_i\right), & \text{if Phase} = \text{Wake} \land \Delta t_{\text{eff}} \leq \tau_{\text{evict}} \\
        \max_{k=1}^{m}(v_{k,d}), & \text{if Phase} = \text{NREM} \land \Delta t_{\text{eff}} > \tau_{\text{evict}} \\
        \text{proj}_{\mathbb{B}_c^{768}}\left(\arg\min\left[-\sum_{(k,v)}\log p(v\mid k, \mathcal{C}'_{+})\right]\right), & \text{if Phase} = \text{REM} \land \Phi_{\text{total}} \leq \tau_{\text{collapse}}
    \end{cases}
    \end{equation}

    \begin{itemize}
        \item \textbf{Wake Phase:} Operates purely in standard Euclidean space, modulating context strictly via the Semantic-Temporal Modulator.
        \item \textbf{NREM Phase:} Synaptic downscaling occurs. The system utilizes a forgetting gate to evict superseded entries and applies Cartesian max-pooling to extract distinct semantic peaks.
        \item \textbf{REM Phase:} Generative replay projects synthetic representations ($\hat{x} = \mathbb{E}[p(x\mid z=m)]$) to isolate the pure semantic ideal, mathematically mapping the result into the non-Euclidean manifold using the Sleep Loss optimization formula:
        \begin{equation}
        \mathcal{L}_{\text{sleep}} = -\sum_{(k,v)\in\mathcal{M}_{\text{current}}} \log p(v\mid k, \mathcal{C}'_{+})
        \end{equation}
    \end{itemize}

    \subsection{The Forced REM Trigger}
    If localized collision density reaches critical limits ($\Phi_{\text{total}} > \tau_{\text{collapse}}$), indicating severe centroid collapse threat, the system instantly fires a hardware interrupt forcing the model into an immediate offline \textbf{Forced REM} phase. This safely shields sub-millisecond response latencies for waking human interaction. To prevent adversarial compute exhaustion (DoS), this hardware interrupt is strictly gated by the Trust No One (TNO) Circuit Breaker (detailed in Section 9.4).
	
	\section{Architectural Topography: Tri-Tiered Chrono-Synchronous Storage}
	The framework optimizes the inherent latency-cost trade-off across three stratified tiers:
	
	\textbf{Tier 1: Chrono-Synchronous Caching (Immediate L1).} Operating purely in Cartesian space, the L1 manages unstructured raw tokens and localized dense foveal arrays, heavily utilizing the Echo Coefficient to prevent KV cache flooding.
	
	\textbf{Tier 2: Euclidean Transition Graph (Transient L2).} Unstructured tokens evicted from L1 undergo Euclidean compaction. Max-pooled Semantic Signatures are interlaced with TF-IDF matrices via Reciprocal Rank Fusion (RRF). It acts as a computational buffer, temporarily housing data prior to the expensive hyperbolic transition.
    
    \textbf{Tier 3: The 768-Dimensional Poincaré Ball (Archival L3).} Historical subgraphs reaching absolute non-volatility ($V_i \to 0$) migrate here. The Colliding Weights Trigger is strictly enforced, restructuring the lifelong knowledge graph permanently into the hyperbolic manifold.

	\subsection{Topological Isomorphism: The Gabriel's Horn Memory Paradox}
	To mathematically formalize the relationship between finite edge-compute constraints and infinite lifelong learning, this tri-tiered architecture perfectly mirrors the topological properties of Gabriel's Horn (Torricelli's trumpet). Generated by revolving the curve $y = \frac{1}{x}$ (for $x \ge 1$) around the x-axis, the figure possesses a strictly finite volume but an absolutely infinite surface area.
	
	\textbf{Finite Volume (The Context Window):} The volume converges to exactly $\pi$. In our framework, this represents the unyielding hardware limits of localized VRAM ($\mathcal{V}_{\text{VRAM}}$) and the transformer's self-attention context window. The probabilistic Imperative Shell can only compute within this finite capacity.
	\begin{equation}
		V = \pi \int_{1}^{\infty} \left(\frac{1}{x}\right)^2 dx = \pi \quad \implies \quad \mathcal{V}_{\text{VRAM}} \le \mathcal{C}_{\text{max}}
	\end{equation}
	
	\textbf{Infinite Surface Area (Hyperbolic Archival):} The surface area diverges to infinity. This mathematically mirrors the Tier 3 Poincaré Ball. While we cannot physically "fill the horn" with the entirety of an agent's lifelong memory (as it would overflow the finite compute volume), we can perpetually map new conversational nodes onto the infinitely expanding hyperbolic manifold (conceptually "painting" the infinite surface).
	\begin{equation}
		A = 2\pi \int_{1}^{\infty} \frac{1}{x} \sqrt{1 + \left(-\frac{1}{x^2}\right)^2} dx \to \infty \quad \implies \quad \mathcal{S}_{\text{Poincar\'e}} \to \infty
	\end{equation}
	
	The Deterministic Functional Core manages the strict translation between this infinite surface and finite volume. Upon encountering a highly salient trigger, the FPGA selectively retrieves necessary semantic "surface points" and deterministically projects them down into the finite "volume" of the Tier 1 cache, seamlessly resolving the bounded-compute/infinite-memory paradox.

	\section{Silicon-Level Isomorphism: FPGA/TPU Hardware Acceleration}
	Attempting to execute highly complex Riemannian metrics (inverse hyperbolic cosines, logarithmic projections) on a standard CPU introduces unacceptable latency spikes. The physical architecture relies on an integrated TPU/FPGA Hybrid System-on-Chip design.
	
    \begin{table}[h]
    \centering
    \caption{Hardware Delegation and Structural Isolation}
    \vspace{0.2cm}
    \begin{tabularx}{\textwidth}{>{\hsize=0.6\hsize\bfseries}X >{\hsize=1.1\hsize}X >{\hsize=1.0\hsize}X >{\hsize=1.3\hsize}X}
    \toprule
    Component & Computational Delegation Profile & Primary Output & Trigger Responsibilities \\
    \midrule
    FPGA (Functional Core) & Deterministic Mathematics, Tie-Breaking, Geometric Projections & Validated 768-dim Vectors, Collision Density Matrices & Monitors Colliding Weights, Executes Hardware Interrupts \\
    \midrule
    TPU (Imperative Shell) & Generative Inference, Natural Language Processing, Transformer Execution & Synthesized Textual Output, Token Generation & None. Operates entirely in a "Dark Silicon" state until invoked by FPGA. \\
    \bottomrule
    \end{tabularx}
    \end{table}

	\subsection{The FPGA as the Deterministic Silicon Functional Core}
	The FPGA exclusively maintains geometric state monitoring, parallelly calculating hyperbolic distances and Ebbinghaus retention weights in strictly bounded clock cycles. When detecting colliding weights, it bypasses software stacks and issues direct hardware-level interrupts to execute Tangent Space projections.
	
	\subsection{The TPU as the Probabilistic Imperative Shell}
	The TPU's matrix-multiplication units remain completely unburdened by structural overhead. It simply receives geometrically stable, mathematically resolved vectors directly from the API Middleware layer, guaranteeing the LLM physically cannot hallucinate its own geometric memory coordinates.

    \section{Advanced Agentic Implications \& Multi-Agent Convergence}
    
    \subsection{Eradication of Metadata Amnesia via Fisher Information}
    By incorporating precise Fisher information metrics alongside hyperbolic distance calculations, the system intelligently weights each 768-dimension strictly by its statistical precision. During Tangent Space Max-Pooling, dimensions bearing high Fisher information (e.g., explicit user security constraints) are heavily amplified, actively surviving the L1 to L3 transition.
    
    \subsection{Langevin Dynamics and Memory Convergence}
    The total memory lifecycle maps cleanly to Riemannian Langevin dynamics on a statistical manifold. Application of the Fokker-Planck equation mathematically guarantees that over an infinite timeline, vectors achieve a highly stable stationary distribution. The system autonomously converges to geometric equilibrium.
    
    \subsection{Resolving Multi-Agent Contradictions via Cellular Sheaves}
    In massively shared multi-agent stores, contradictory facts (e.g., Sensor A says "Operational", Sensor B says "Offline") geometrically manifest as highly non-trivial first cohomology classes within a complex cellular sheaf. The colliding weights trigger detects this severe structural friction. Instead of applying max-pooling, it mathematically isolates the conflict and safely escalates to the Imperative Shell for human-in-the-loop arbitration.

	\section{Theorized Elements and Empirical Validation}
	
	\subsection{Graph-Augmented LLM Pre-Training}
	Applying Graph Attention Network (GAT) weights directly to CCMA DAG elements during LLM fine-tuning allows smaller models ($\leq 1.5\text{B}$ parameters) to achieve near-optimal recall of historical states.
	
	\subsection{Macro-to-Micro Spatial Decomposition in VLMs}
	Visual data processing utilizes the macro-embedding $E_{\text{macro}}$ as a compute gate. If cosine similarity exceeds $\tau_{\text{explore}}$, the algorithm triggers divisive segmentation $S(I) \to \{I_{\text{sub1}}, \dots, I_{\text{subk}}\}$.
	
	\subsection{Return on Comprehension (RoC)}
	High-capacity models produce segmented correlation weights via recursive scrutiny:
	\begin{equation}
		RoC = \sum_{i=1}^{n} \left( w_i \cdot \text{CosineSim}(E_{\text{micro}, i}, E_{\text{historic}, i}) \right)
	\end{equation}
	
	\subsection{Bi-Temporal Visual Object Permanence}
	Sequential diagnostic images yield extreme similarities due to identical backgrounds. CCMA enforces Visual Object Permanence via a Structural Similarity (SSIM) Delta Check prior to DAG ingestion.
	
	\subsection{Agentic Edge-to-Cloud Escalation}
	Upon exceeding local VRAM, the edge node transmits semantically compressed DAG Bindles. Cloud resolution is ingested back into the local DAG, establishing \textbf{Continuous Local Learning} and exponentially decaying cloud dependencies.

	\subsection{Geo-Temporal Anomaly Detection via Foveated Semantic Scrutiny}
	The system extracts high-resolution foveal crops using a Laplacian Pyramid base layer acting as a low-resolution gating frame, reducing latency while preserving computational bandwidth for deep anomaly detection.
    
	\section{Addendums: Isolation and Security}
	
	\subsection{Deterministic Payload Segmentation (DPS)}
	To prevent catastrophic truncation, DPS explicitly routes file attachments and large structural code blocks into immutable \texttt{NamedTuple} arrays, replaced in the main prompt by lightweight Semantic Pointers (e.g., \texttt{[Bindle\_Ref: 0x8F2A]}). For massive continuous text payloads, DPS maps strings to Abstract Syntax Trees (AST) and executes deterministic token-aware sliding windows for optimal unstructured paging.
	
	\subsection{Multi-User Context Isolation via Role-Based Semantic Masking}
	Every Semantic Signature is bound to an immutable authorization tuple: $(H_{\text{user}}, R_{\text{mask}})$. During graph traversal, the system applies Role-Based Semantic Masking (RBSM) via a pure bitwise \texttt{AND} operation:
	\begin{equation}
		M_{\text{auth}}(v) = (U_{\text{roles}} \land R_{\text{mask}}(v)) \neq 0
	\end{equation}
	Unauthorized queries mathematically return a cosine distance of infinity.
	
	\subsection{Zero-Trust Sanitization \& API Middleware (The Functional Proxy)}
	CCMA is deployed strictly as an LLM API Middleware Layer. It implements a \textbf{Zero-Trust Tokenization Loop} extracting PII and substituting it with FNV-1a 64-bit nonces (e.g., \texttt{[[REF-22b8ce99a0ef5878]]}) prior to inference. Post-generation, the deterministic core safely rehydrates the payload strictly bound to authorized UI endpoints, physically prohibiting the LLM from executing systemic data exfiltration.

	\subsection{Trust No One (TNO): Mitigating Adversarial REM-Forcing (Compute Exhaustion DoS)}
	A critical vulnerability in dynamic memory consolidation is the threat of Adversarial REM-Forcing. A bad actor could theoretically craft a payload of hyper-dense, semantically overlapping nonsense designed specifically to continuously trigger $\Phi_{\text{total}} > \tau_{\text{collapse}}$. This would force the system into a perpetual offline REM loop, effectively causing a Denial of Service (DoS) via compute exhaustion on the local edge hardware.
	
	To neutralize this, the FPGA implements a hardware-level \textbf{TNO Circuit Breaker} utilizing an immutable, stateless token bucket protocol combined with Topological Entropy Scoring ($H_{\text{topo}}$). Before a Forced REM interrupt is authorized, the Functional Core strictly evaluates the density request:
	\begin{equation}
		\text{REM}_{\text{auth}} = 
		\begin{cases} 
			\text{Execute}, & \text{if } C_{\text{rem}} < R_{\text{max}} \land H_{\text{topo}}(\mathcal{C}'_{+}) > \tau_{\text{organic}} \\
			\text{Quarantine}, & \text{otherwise}
		\end{cases}
	\end{equation}
	If the trigger rate $C_{\text{rem}}$ exceeds the maximum temporal threshold $R_{\text{max}}$, or if the colliding vectors exhibit the unnatural topological uniformity characteristic of an adversarial injection ($H_{\text{topo}} \leq \tau_{\text{organic}}$), the interrupt is instantly denied. The offending payload is deterministically shunted into an isolated ``Euclidean Quarantine Shard,'' preserving base system latency and permanently locking out the malicious vector trajectory without ever engaging the probabilistic Imperative Shell.

	\begin{thebibliography}{16}
		\bibitem{vaswani2017} Vaswani, A., et al. (2017). \textit{Attention Is All You Need}. NIPS.
		\bibitem{ebbinghaus1885} Ebbinghaus, H. (1885). \textit{Memory: A Contribution to Experimental Psychology}. 
        \bibitem{yan2024crag} Yan, S., et al. (2024). \textit{Corrective Retrieval Augmented Generation}. arXiv.
		\bibitem{malkov2018hnsw} Malkov, Y. A., \& Yashunin, D. A. (2018). \textit{Efficient and robust approximate nearest neighbor search using HNSW}. IEEE TPAMI.
		\bibitem{microsoft2024graphrag} Edge, D., et al. (2024). \textit{From Local to Global: A Graph RAG Approach}. Microsoft Research.
		\bibitem{nurvitadhi2017fpga} Nurvitadhi, E., et al. (2017). \textit{Can FPGAs beat GPUs in Accelerating Next-Generation DNNs?}. FPGA.
		\bibitem{synth_temporal} The Opinionated Geek. \textit{It's About Time: Temporal Weighting in LLM Chats}. Medium.
	\end{thebibliography}
	
\end{document}
